% !TeX root = ./Thesis.tex
% -- TemplateKnob

% -----------------------------------------------------------------------
%   >> Personal Information to be filled in by thesis author !!!   <<
% -----------------------------------------------------------------------
\newcommand{\myTitle}{HiPS: Steganography in chat messages using local large language models on Android}
\newcommand{\myDegree}{Bachelor's Thesis}
\newcommand{\myVersion}{0.1}
\newcommand{\myName}{Tobias Vonderheidt}
\newcommand{\mySupervisor}{M.Sc. Nils Rollshausen}
\newcommand{\myThesiscode}{SEEMOO-BSC-$0368$}           % You will get this from our secretary
\newcommand{\myTime}{\formatdate{09}{05}{2025}}         % hand-in date of the thesis
\newcommand{\myAbstract}{While you read this sentence, around one million WhatsApp messages are being sent. We share the details of our personal lives in them, from our highest hopes to our deepest fears. This is only possible because we assume them to be private. To protect user privacy, we implement an Android app called Hiding in Plain Sight (HiPS). It creates a layer of protection currently missing from popular instant messengers: Steganography. We run large language models (LLMs) locally on the smartphone to encode secret messages into unsuspicious cover texts. Our work is based on the Stegasuras project. We extend its functionality in multiple ways: By porting it to llama.cpp, we are able to swap LLMs to scale with available hardware. We create chat conversations of arbitrarily interleaved cover texts and plain texts, expose a system prompt for easy low-level access to the LLM via natural language, and enrich cover texts with emojis to make them more organic. To compare our cover texts to real chat messages, we conduct a survey amongst students of TU Darmstadt. This delivers valuable insights in how to fine-tune cover text quality for this highly relevant demographic of users.} % at the very end, put "clean" abstract here
\newcommand{\myYearPublication}{2025}                   % year of publication (for copyright and footer)


% -----------------------------------------------------------------------
% General Information of SEEMOO and the TU Darmstadt.
% -----------------------------------------------------------------------
\newcommand{\myFaculty}{Department of Computer Science}
\newcommand{\myFacultyDE}{Fachbereich Informatik}
\newcommand{\myDepartment}{Secure Mobile Networking Lab}
\newcommand{\myDepartmentDE}{Fachgebiet Sichere Mobile Netze}
\newcommand{\myUni}{\protect{Technische Universität Darmstadt}}
\newcommand{\myUniKennziffer}{D17}
\newcommand{\myLocation}{Darmstadt}


% -----------------------------------------------------------------------
% The following are only required to be filled in for PhD Theses.
% -----------------------------------------------------------------------
\newcommand{\myURN}{urn:nbn:de:tuda-tuprints-83253}
\newcommand{\myDegreePhD}{Doktor-Ingenieur (Dr.-Ing.)}
\newcommand{\myBirthDate}{\formatdate{1}{1}{1970}}
\newcommand{\myBirthPlace}{Darmstadt, Deutschland}
\newcommand{\myNationality}{German}
\newcommand{\myProf}{Prof. Dr.-Ing. Matthias Hollick}
\newcommand{\myOtherProf}{Put name here}
\newcommand{\myYearPresent}{1337}                                % year of disputation
\newcommand{\myTimePresent}{\formatdate{01}{01}{\myYearPresent}} % date of disputation