% !TeX root = ../Thesis.tex

%*******************************************************
\chapterExtra{Collaborations and My Contribution}
%*******************************************************
\label{ch:Collaborations}

% From Daniel Steinmetzer's dissertation
Systematically investigating a technical research topic and engineering the required tools is a demanding and interdisciplinary process. Most achievements could never evolve without collaborations in which colleagues and international partners integrated their intellectual forces. When working in teams, accounting particular contributions and components of the resulting publications to individual collaborators becomes almost impossible. This situation also applies to several contents of this thesis, which arise from collaborations, thus, cover joint contributions. Many of these collaborations persisted even longer than the research projects and became a long-term strategic partnership.
In our previous publications, all authors contributed by discussing ideas and debating on results throughout the whole project duration. Each of them has particular strengths that sometimes appear invisible. For this reason, I explicitly state and acknowledge---where possible---the contributions of my collaborators in the following.

% From Milan Stute's dissertation
In the following, I detail the contributions of my co-authors and myself per chapter. In addition, I follow the regulations of the \myFaculty{} at \myUni{} and give an account of the parts that include verbatim or revised fragments of previous publications that form this thesis as indicated in the preceding list of publications.\footnote{References in this chapter refer to my list of publications given on \cpagerefrange*{ch:AuthorPublications}{ch:AuthorPublicationsEnd}.}

\sloppy

\Cref{ch:introduction,ch:relatedwork} collate the contributions, background, and related work sections of the core papers that form this thesis~\cite{Stute2018a,Stute2020}.

% etc etc etc

\fussy

\label{ch:CollaborationsEnd}